---
title: "Assignment 5 - Meta-analysis of pitch in schizophrenia"
author: "Riccardo Fusaroli"
date: "3/7/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

locpath= "C:/Users/nanna/OneDrive - Aarhus universitet/3. Semester/Experimental Methods 3/Metaanalysis/Assignment5_MetaAnalysis"

setwd(locpath)


library(pacman)
p_load(tidyverse, metafor, lme4, lmerTest, plyr)

```

# Building on the shoulders of giants: meta-analysis

## Questions to be answered

1. What is the current evidence for distinctive patterns of pitch mean and pitch sd in schizophrenia? 

Report how many papers report quantitative estimates, your method to analyze them, the estimated effect size of the difference (mean effect size and standard error for pitch mean, same for pitch sd) and forest plots representing it. 

2. Do the results match your own analysis from Assignment 3? If you add your results to the meta-analysis, do the estimated effect sizes change? 

Report the new estimates and the new forest plots.

3. Assess the quality of the literature: report and comment on heterogeneity of the studies (tau, I2), on publication bias (funnel plot), and on influential studies.

## Tips on the process to follow:

- Download the data on all published articles analyzing pitch in schizophrenia (on gitlab)
```{r + Load data}

data = read.csv("SR_SCHIZO.csv")

```


- Look through the dataset to find out which columns to use, and if there is any additional information written as comments (real world data is always messy!).

    * Hint: Make sure you read the comments in the columns: `pitch_f0_variability`, `frequency`, `Title`,  `ACOUST_ANA_DESCR`, `DESCRIPTION`, and `COMMENTS`
    
```{r + Excluding studies}

#We exluce all studies in which only sample size is reported. 

data_clean <- data[!with(data,is.na(PITCH_F0_SZ_SD) & is.na(PITCH_F0SD_SZ_SD)),]

#data_clean$ACOUST_ANA_DESCR

```


- Following the procedure in the slides calculate effect size and standard error of the effect size per each study. N.B. we focus on pitch mean and pitch standard deviation.

 . first try using lmer (to connect to what you know of mixed effects models)
 . then use rma() (to get some juicy additional statistics)

- Build a forest plot of the results (forest(model))


```{r + Cohens D}

#Cohens D for mean
pitch_mean = escalc('SMD', n1i=SAMPLE_SIZE_SZ, n2i=SAMPLE_SIZE_HC, m1i=PITCH_F0_SZ_M, m2i=PITCH_F0_HC_M, sd1i=PITCH_F0_SZ_SD, sd2i=PITCH_F0_HC_SD, data = data_clean)

pitch_var = escalc('SMD', n1i=SAMPLE_SIZE_SZ, n2i=SAMPLE_SIZE_HC, m1i=PITCH_F0SD_SZ_M, m2i=PITCH_F0SD_HC_M, sd1i=PITCH_F0SD_SZ_SD, sd2i=PITCH_F0SD_HC_SD, data = data_clean)

```


```{r + Models + rma}

# Mixed effects model 
model_mean <- lmer(yi ~ 1 + (1 | StudyID), weights = 1/vi, data= pitch_mean, control=lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))
summary(model_mean)

model_var <- lmer(yi ~ 1 + (1 | StudyID), weights = 1/vi, data= pitch_var, control=lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))
summary(model_var)


# Meta-analysis optimisation
model_mean_1 <- rma(yi, vi, data = pitch_mean, slab=StudyID)
model_mean_1

forest(model_mean_1)
confint(model_mean_1)

model_var_1 <- rma(yi, vi, data = pitch_var, slab=StudyID)
model_var_1
forest(model_var_1)
confint(model_var_1)


```


```{r + Infuencial points}

inf_mean <- influence(model_mean_1)
print(inf_mean)
plot(inf_mean)

inf_var <- influence(model_var_1)
print(inf_var)
plot(inf_var)



```


```{r + Funnel plots}

funnel_mean <- funnel(model_mean_1, main = "Random-Effects Model", xlab = "Standardized Mean Difference")

funnel_var = funnel(model_var_1, main = "Random-Effects Model", xlab = "Standardized Mean Difference")


regtest(model_mean_1)
ranktest(model_mean_1)


regtest(model_var_1)
ranktest(model_var_1)

```

 
- Go back to Assignment 3, add your own study to the data table, and re-run meta-analysis. Do the results change?

      Our study is 3 in 1
      Model: pitch ~ diagnosis (1| Study)

      Use the predict funtion to get the best estimates
      Since we have study as random effect 

- Now look at the output of rma() and check tau and I2

##Adding Assignment 3

```{r + Read data from assignment 3 + getting means from models}

data_ass3 <- read.csv("data_with_demo.csv")



#Caculating the number in each group 

data_ass3 %>% 
  group_by(ID) %>%
  dplyr::filter(diagnosis == "Control" & study == "1") %>%
  summarise() %>%
  nrow()
#[1] 352

data_ass3 %>% 
  group_by(ID) %>%
  filter(diagnosis == "Schizophrenia" & study == 1) %>%
  summarise() %>%
  nrow()
#[1] 335

data_ass3 %>% 
  group_by(ID) %>%
  filter(diagnosis == "Control" & study == 2) %>%
  summarise() %>%
  nrow()
#[1] 184

data_ass3 %>% 
  group_by(ID) %>%
  filter(diagnosis == "Schizophrenia" & study == 2) %>%
  summarise() %>%
  nrow()
#[1] 182

data_ass3 %>% 
  group_by(ID) %>%
  filter(diagnosis == "Control" & study == 4) %>%
  summarise() %>%
  nrow()
#[1] 128

data_ass3 %>% 
  group_by(ID) %>%
  filter(diagnosis == "Schizophrenia" & study == 4) %>%
  summarise() %>%
  nrow()
#[1] 158
```


```{r + getting means from models from ass3}
#Making models 

model_ass3_mean <- lmer(mean ~ diagnosis + (1|trial) + (1|study) + (1|ID), data_ass3)
model_ass3_sd <- lmer(sd ~ diagnosis + (1|study) + (1|trial) +(1|ID), data_ass3)

diagnosis <- c("Control", "Control", "Control", "Schizophrenia", "Schizophrenia", "Schizophrenia")
study <- c(1:3, 1:3)
diag_stud <- as.data.frame(diagnosis)
diag_stud$study <- study

#Get optimal "mean" by predicting data for a matrix for 3 studies
predict(model_ass3_mean, re.form = ~ (1| study),  newdata = diag_stud, allow.new.levels = T)


predict(model_ass3_sd, re.form = ~ (1| study),  newdata = diag_stud, allow.new.levels = T)


sd_mean <- data_ass3 %>% 
   dplyr::group_by(diagnosis, study) %>%
   dplyr::summarise(sd = sd(mean))

sd_sd <- data_ass3 %>% 
   dplyr::group_by(diagnosis, study) %>%
   dplyr::summarise(sd = sd(sd))



#Adding values to a dataframe with similar columns

listoflists <- list(StudyID = c(49, 50, 51), 
                    ArticleID = 47, 
                    SAMPLE_SIZE_HC = c(36, 23, 16),
                    SAMPLE_SIZE_SZ = c(34, 23, 19), 
                    
                    PITCH_F0_HC_M = c(142.4939, 123.8641, 137.0162),
                    PITCH_F0_SZ_M = c(156.2813, 137.6516, 150.8036), 
                    
                    PITCH_F0_HC_SD = c(51.03645, 34.76154, 46.62267),
                    PITCH_F0_SZ_SD = c(54.74809, 60.50305, 46.65587),
                    
                    PITCH_F0SD_HC_M = c(24.72409, 27.32127, 25.47117),
                    PITCH_F0SD_SZ_M = c(22.07029, 24.66747, 22.81737),
                    
                    PITCH_F0SD_HC_SD = c(15.79852, 20.48901, 21.31672),
                    PITCH_F0SD_SZ_SD = c(29.54196, 47.36456, 12.57604))

ass3 <- as.data.frame(listoflists)

ass3$ACOUST_ANA_DESCR = NA
ass3$DESCRIPTION = NA
ass3$COMMENTS = "At least we tried"
ass3$frequency = NA
ass3$Title = "Diagnosis On Basis of Pitch"
ass3$Authors = "CogSci et al"
ass3$Article = NA
ass3$Year_publication = "2018"
ass3$pitch_f0_variability = NA 

# as.factor(ass3$ACOUST_ANA_DESCR)
# as.factor(ass3$DESCRIPTION)
# as.factor(ass3$COMMENTS)
# as.factor(ass3$frequency)
# as.factor(ass3$Title)
# as.factor(ass3$Authors)
# as.factor(ass3$Article)

data_all <- rbind(data_clean, ass3)

```


```{r + Cohens D and models and rma}

#Cohens D for mean
pitch_mean_all = escalc('SMD', n1i=SAMPLE_SIZE_SZ, n2i=SAMPLE_SIZE_HC, m1i=PITCH_F0_SZ_M, m2i=PITCH_F0_HC_M, sd1i=PITCH_F0_SZ_SD, sd2i=PITCH_F0_HC_SD, data = data_all)

pitch_var_all = escalc('SMD', n1i=SAMPLE_SIZE_SZ, n2i=SAMPLE_SIZE_HC, m1i=PITCH_F0SD_SZ_M, m2i=PITCH_F0SD_HC_M, sd1i=PITCH_F0SD_SZ_SD, sd2i=PITCH_F0SD_HC_SD, data = data_all)


# Mixed effects model 
model_mean_all <- lmer(yi ~ 1 + (1 | StudyID), weights = 1/vi, data= pitch_mean_all, control=lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))

summary(model_mean_all)

model_var_all <- lmer(yi ~ 1 + (1 | StudyID), weights = 1/vi, data= pitch_var_all, control=lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))
summary(model_var_all)

# Meta-analysis optimisation
model_mean_2 <- rma(yi, vi, data = pitch_mean_all, slab=StudyID)
model_mean_2
forest(model_mean_2)
confint(model_mean_2)


model_var_2 <- rma(yi, vi, data = pitch_var_all, slab=StudyID)
model_var_2
forest(model_var_2)
```


```{r + Infuencial points for data_all}

inf_mean_all <- influence(model_mean_2)
print(inf_mean_all)
plot(inf_mean_all)

inf_var_all <- influence(model_var_2)
print(inf_var_all)
plot(inf_var_all)



```


```{r + funnel plots for data_all}

funnel_mean_all <- funnel(model_mean_2, main = "Random-Effects Model", xlab = "Standardized Mean Difference")

funnel_var_all = funnel(model_var_2, main = "Random-Effects Model", xlab = "Standardized Mean Difference")

regtest(model_mean_2)
ranktest(model_mean_2)

regtest(model_var_2)
ranktest(model_var_2)

```



```{r + Excluding 15 and plotting}

#Plots with exclusion of study 15
test_var <- pitch_var_all[!pitch_var_all$StudyID == 15,]

model_var_3 <- rma(yi, vi, data = test_var, slab=StudyID)
model_var_3

forest(model_var_3)
funnel_var_all_v2 = funnel(model_var_3, main = "Random-Effects Model", xlab = "Standardized Mean Difference")

```






